---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "**`[[`**Hao_YU**`]]`**"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```


I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_count, aes(x = date, y = Cases)) + geom_point()
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe?
```{r}
ggplot(covid_data_count, aes(x= log(Cases), y = race, color=race)) +
  geom_boxplot(varwidth = TRUE)+
  theme(legend.position = "none")
```

2. Are there any conclusions you can draw?
Overall, NHPI and AIAN have a smaller number of cases, while White and Latinx have a larger number of cases. Others and Asians show a wider spread in terms of IQR and whisker length, whereas White and Latinx have smaller whisker lengths.

3. What were you not able to do due to not having the R knowledge?
I am unable to remove the 'total' variable in the visualization. This variable is too large to visualize the cases among specific races, which hinders my ability to focus on a more detailed analysis of those specific races.

4. What other data would be useful to better understand this data?
The age of each COVID case may be useful for analyzing the situation of cases among different races. Additionally, it should also include the number of people in each race for comparison, as some races may have a large population, resulting in a higher number of cases


